\section{Conventions}\label{conventions}\label{core}\label{help}

Conventions augment and enable \keyword{expansions} or are found to be helpful.
%
\begin{itemize}
    \item The \texttt{core} loads the \keyword{plugins} and \keyword{terraforms} the \keyword{machine}.
    \item \texttt{<command> help} shows help about \keyword{command}.
    \item \texttt{@ref} is an alias for \texttt{@cache read} that enables \texttt{\$(@ref <keyword>)} and, thus, object alias~\footnote{Refer to~\url{https://github.com/kamangir/roofAI/blob/main/roofAI/semseg/README.md} for an example.}.
\end{itemize}  

\subsection{\texttt{\$<core>\_<suffix>}}\label{awareness}

During initialization, the \keyword{core} and the \keyword{plugins} set a series of variables to harmonize paths and other \keyword{machine}--specific parameters to enable the same code to run on different machines simultaneously. 
%
\begin{itemize}
    \item{\texttt{\$<core>\_git\_<suffix>}: \keywordd{@git}{git}.}
    \item{\texttt{\$<core>\_<type>\_name[\_prev[n]]}: \keyword{select}ed objects.}
    \item{\texttt{\$<core>\_<type>\_path}: \keyword{select}ed object path.}
    \item{\texttt{\$<core>\_is\_<suffix>} describe the \keyword{machine}}
    \item{\texttt{\$<core>\_path\_<suffix>}: paths.}
\end{itemize}
%
An alias of \texttt{env} lists these variables.
%
\begin{verbatim}
@env [<keyword>]
\end{verbatim}

This mechanism is also relevant to functions~\cite{namespaces}.

\subsection{\texttt{dryrun}}\label{dryrun}

In \texttt{dryrun} mode, the low-cost and fast aspects of the command are executed, and the rest of the operation is logged instead. \texttt{@eval} is used for this operation. 

\input{conventions/param_injection}
\input{conventions/delim}

\subsection{\texttt{@init}}\label{init}

The following expansions initialize the \keyword{core}, and therefore all \keyword{plugins}, or \texttt{<plugin-name>}.
%
\begin{verbatim}
@init <options>

<plugin-name> init <options>
\end{verbatim}

\subsection{Plugins}\label{plugins}

A plugin generally defines one or more \keyword{callables}.

\subsection{\texttt{@start}}\label{start}

\begin{verbatim}
@start <options>
\end{verbatim}

\subsection{\texttt{@conda}}\label{conda}

\begin{verbatim}
@conda create [clone=<base>,name=<environment-name>,~recreate]

@conda exists [<environment-name>]

@conda list

@conda remove|rm [<environment-name>]
\end{verbatim}

\subsection{\texttt{@publish}}\label{publish}

\begin{verbatim}
@publish [extension=<png>,filename=<filename-1+filename-2>,randomize,tar] \
    [.|<object-name>]
\end{verbatim}
%
copies select content from \texttt{<object-name>} into a publicly accessible bucket.


